A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-15 manuscript/manuscript.tex
minor rewording

We present Arcana, a software framework to facilitate the development of
comprehensive analysis suites for neuroimaging data that implement
complete workflows from repository data to publication results. The
encapsulation of repository data and workflow generation in Arcana
enables researchers to create robust workflows while focussing on the
core logic of their analysis. Arcana's modular pipeline and OO
architecture promotes code reuse between different workflows by
facilitating the sharing of common segments (e.g. registration,
segmentation). The clear separation of analysis design from its
application leads to portable workflows, which can be applied to
datasets stored in a number of storage systems. In addition, the
management of intermediate derivatives, provenance and software
versioning, coupled with ability to submit jobs to HPC clusters, enables
workflows implemented in Arcana to scale to large datasets. Arcana
thereby enables researchers to quickly prototype analysis suites on
local workstations that can be deployed on enterprise-scale
infrastructure without modification.

@@

A level of proficiency in Python OO design is required to design new
analyses in Arcana, which may preclude inexperienced programmers.
However, only a basic knowledge of Python is required to apply existing
analyses to new datasets. Furthermore, a number of example Study classes
have been implemented, which can guide the hand of analysis designers.
Arcana imposes a consistent structure on workflows implemented within
it, making the code easier to understand for developers who are familiar
with the framework. In addition, class inheritance provides a manageable
way to adapt and extend to existing analyses and highlights where
modified analyses differ from standard procedures.

>>>>

We present Arcana, a software framework to facilitate the development of
comprehensive analysis suites for neuroimaging data that implement
complete workflows from repository data to publication results. The
encapsulation of repository data and workflow generation in Arcana
enables researchers to create robust workflows while focussing on the
core logic of their analysis. Arcana's modular pipeline and OO
architecture promotes code reuse between different workflows by
facilitating the sharing of common segments (e.g. registration,
segmentation). The clear separation of analysis design from its
application leads to portable workflows, which can be applied to
datasets stored in a number of storage systems. In addition, the
management of intermediate derivatives, provenance and software
versioning, coupled with ability to submit jobs to HPC clusters, enables
workflows implemented in Arcana to scale to large datasets. Arcana
thereby enables researchers to quickly prototype analysis suites on
local workstations that can be deployed on large-scale
infrastructure without modification.

@@

A level of proficiency in Python OO design is required to implement new
analyses in Arcana, which may preclude inexperienced programmers.
However, only a basic knowledge of Python is required to apply existing
analyses to new datasets. Furthermore, a number of example Study classes
have been implemented, which can guide the hand of analysis designers.
Arcana imposes a consistent structure on workflows implemented within
it, making the code easier to understand for developers who are familiar
with the framework. In addition, class inheritance provides a manageable
way to adapt and extend to existing analyses and highlights where
modified analyses differ from standard procedures.
